My title

### 2024-11-04 paper/paper.qmd
Discussion update

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

@@

Please don't use these as sub-heading labels - change them to be what your point actually is.

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-pollingharris
#| fig-cap: "Polling for Harris By State"

@@

Arizona is a very important swing state especially as the state has switches which party they voted for in in the last two elections with Trump winning 49% of the vote and Clinton with 45.5%, which considering Arizona is a swing state is a rather significant6 margin. While in the 2020 election Biden ended up winning Arizona with 49.4% of the vote and Trump 49.1%, which is a much smaller margin of victory and what makes Arizona so questionable in the 2024 election. We can see in @fig-pollingharris that while the polling numbers for Harris started somewhat low around 42%, the have gone up significantly and have continued to trend upwards in the most recent polls. Although, in the @fig-supportstate trump still has larger support in the state, and the largest polling difference in Trump's favour out of all the swing states polled.

We believe Arizona will vote: **IDK**

@@

Considering the last two elections Georgia is very similar to Arizona, as in 2016 Trump won the state with 50.8% to Clinton's 45.6%. While in the 2020 election Biden won with a slim victory of 49.5% to Trump's 49.3%, which again is very similar to Arizona's last two election results with significant republican victory in 2016 and a rather marginal win in 2020, which was the first democratic victory for the state since 1992. Georgia is in an interesting situation as lot of the democratic vote in the state comes from the black community, although Harris a has less support from male black population, which could very realistically result in a Trump victory in the state in the upcomming election.
